Paper Figure Generation

### 2023-08-15 R/PaperFigureGeneration.rmd
Added atypical position filtering figure

```{r figure_S13, fig.width = 6, fig.height = 5}
print(paste0("1h C>T Read Length Slope: ", getReadLengthSlope(NHF1PairedCutSiteDistances$`1h`$C_to_T)))
plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`1h`$C_to_T, READ_LENGTH,
                           title = "NHF1 1h C>T All Reps TGG-filtered",
                           xlim = c(10.5, 26.5), ylim = c(17.5, 33.5),
                           xAxisBreaks = seq(11,26,3), yAxisBreaks = seq(18,33,3))
print(paste0("1h C>T Coupling: ", getCouplingRate(NHF1PairedCutSiteDistances$`1h`$C_to_T)*-100, '%'))
plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`1h`$C_to_T, THREE_PRIME_CUT_SITE_DISTANCE,
                           title = "NHF1 1h C>T All Reps TGG-filtered",
                           xlim = c(10.5,26.5), ylim = c(0,16),
                           xAxisBreaks = seq(11,26,3), yAxisBreaks = seq(0,15,3))

@@

```{r figure_S14, fig.width = 6, fig.height = 5}
print(paste0("Arabidopsis CC>TT read length slope: ", getReadLengthSlope(arabidopsisPairedCutSiteDistances$ZT2$CC_to_TT)))
plotPairedCutSiteDistances(arabidopsisPairedCutSiteDistances$ZT2$CC_to_TT, READ_LENGTH,
                           title = "Arabidopsis ZT2 CC>TT All Reps TGG-filtered",
                           xlim = c(15,25), ylim = c(22,32), yAxisBreaks = c(23,25,27,29,31))
print(paste0("Arabidopsis CC>TT Coupling: ", getCouplingRate(arabidopsisPairedCutSiteDistances$ZT2$CC_to_TT)*-100, '%'))
plotPairedCutSiteDistances(arabidopsisPairedCutSiteDistances$ZT2$CC_to_TT, THREE_PRIME_CUT_SITE_DISTANCE,
                           title = "Arabidopsis ZT2 CC>TT All Reps TGG-filtered",
                           xlim = c(15,25), ylim = c(3,13), yAxisBreaks = c(4,6,8,10,12))

@@

```{r figure_S15A, fig.width = 10, fig.height = 5}
plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances$`8h`$three_prime,
                          plotCutSiteSignificance = FALSE,
                          FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
                          countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
                          meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances$`1h`$five_prime,
                          cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
                          title = "NHF1 8h C>T All Reps TGG-Filtered Strand-Aligned",
                          xAxisLabel = "Dyad-Relative Position", xlim = c(-200, 200),
                          secondaryAxisBreaks = seq(19,19.8,0.2),
                          meanCutSiteDistanceMax = 19.825, meanCutSiteDistanceMin = 18.975)
```
```{r figure_S15B}
plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances$`8h`$three_prime,
                          FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
                          countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
                          meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances$`1h`$five_prime,
                          cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
                          title = "NHF1 8h C>T All Reps TGG-Filtered Strand-Aligned",
                          xAxisLabel = "Dyad-Relative Position", xlim = c(-100, -40),
                          secondaryAxisBreaks = seq(19,19.8,0.2),
                          meanCutSiteDistanceMax = 19.825, meanCutSiteDistanceMin = 18.975)
```
```{r figure_S15C}
plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances$`8h`$three_prime,
                          FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
                          countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
                          meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances$`1h`$five_prime,
                          cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
                          title = "NHF1 8h C>T All Reps TGG-Filtered Strand-Aligned",
                          xAxisLabel = "Dyad-Relative Position", xlim = c(40, 100),
                          secondaryAxisBreaks = seq(19,19.8,0.2),
                          meanCutSiteDistanceMax = 19.825, meanCutSiteDistanceMin = 18.975)
```

>>>>

```{r read_figure_S13_data}
NHF1PairedCutSiteDistances$`1h`$Non_C_to_T_Position_Filtered = fread(generateFilePath(
  NHF1CutSiteCorrelationDirectory, dataTypeStrings$pairedCutSiteDistances, ".tsv",
  cellType = "NHF1", lesion = "CPD", timepoint = "1h",
  repitition = "all_reps", filtering = "TGG_filtered",
  omittedMismatches = "C>T", additionalInformation = "atypical_position_filtering"
))
```

```{r figure_S13, fig.width = 6, fig.height = 5}
print(paste0("1h non-C>T Read Length Slope: ", getReadLengthSlope(NHF1PairedCutSiteDistances$`1h`$Non_C_to_T_Position_Filtered)))
plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`1h`$Non_C_to_T_Position_Filtered, READ_LENGTH,
                           title = "NHF1 1h Non-C>T Position-Filtered All Reps TGG-filtered",
                           xlim = c(10.5, 26.5), ylim = c(17.5, 33.5),
                           xAxisBreaks = seq(11,26,3), yAxisBreaks = seq(18,33,3))
print(paste0("1h non-C>T Coupling: ", getCouplingRate(NHF1PairedCutSiteDistances$`1h`$Non_C_to_T_Position_Filtered)))
plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`1h`$Non_C_to_T_Position_Filtered, THREE_PRIME_CUT_SITE_DISTANCE,
                           title = "NHF1 1h Non-C>T Position-Filtered All Reps TGG-filtered",
                           xlim = c(10.5,26.5), ylim = c(0,16),
                           xAxisBreaks = seq(11,26,3), yAxisBreaks = seq(0,15,3))
```

```{r figure_S14, fig.width = 6, fig.height = 5}
print(paste0("1h C>T Read Length Slope: ", getReadLengthSlope(NHF1PairedCutSiteDistances$`1h`$C_to_T)))
plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`1h`$C_to_T, READ_LENGTH,
                           title = "NHF1 1h C>T All Reps TGG-filtered",
                           xlim = c(10.5, 26.5), ylim = c(17.5, 33.5),
                           xAxisBreaks = seq(11,26,3), yAxisBreaks = seq(18,33,3))
print(paste0("1h C>T Coupling: ", getCouplingRate(NHF1PairedCutSiteDistances$`1h`$C_to_T)*-100, '%'))
plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`1h`$C_to_T, THREE_PRIME_CUT_SITE_DISTANCE,
                           title = "NHF1 1h C>T All Reps TGG-filtered",
                           xlim = c(10.5,26.5), ylim = c(0,16),
                           xAxisBreaks = seq(11,26,3), yAxisBreaks = seq(0,15,3))

@@

```{r figure_S15, fig.width = 6, fig.height = 5}
print(paste0("Arabidopsis CC>TT read length slope: ", getReadLengthSlope(arabidopsisPairedCutSiteDistances$ZT2$CC_to_TT)))
plotPairedCutSiteDistances(arabidopsisPairedCutSiteDistances$ZT2$CC_to_TT, READ_LENGTH,
                           title = "Arabidopsis ZT2 CC>TT All Reps TGG-filtered",
                           xlim = c(15,25), ylim = c(22,32), yAxisBreaks = c(23,25,27,29,31))
print(paste0("Arabidopsis CC>TT Coupling: ", getCouplingRate(arabidopsisPairedCutSiteDistances$ZT2$CC_to_TT)*-100, '%'))
plotPairedCutSiteDistances(arabidopsisPairedCutSiteDistances$ZT2$CC_to_TT, THREE_PRIME_CUT_SITE_DISTANCE,
                           title = "Arabidopsis ZT2 CC>TT All Reps TGG-filtered",
                           xlim = c(15,25), ylim = c(3,13), yAxisBreaks = c(4,6,8,10,12))

@@

```{r figure_S16A, fig.width = 10, fig.height = 5}
plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances$`8h`$three_prime,
                          plotCutSiteSignificance = FALSE,
                          FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
                          countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
                          meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances$`1h`$five_prime,
                          cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
                          title = "NHF1 8h C>T All Reps TGG-Filtered Strand-Aligned",
                          xAxisLabel = "Dyad-Relative Position", xlim = c(-200, 200),
                          secondaryAxisBreaks = seq(19,19.8,0.2),
                          meanCutSiteDistanceMax = 19.825, meanCutSiteDistanceMin = 18.975)
```
```{r figure_S16B}
plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances$`8h`$three_prime,
                          FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
                          countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
                          meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances$`1h`$five_prime,
                          cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
                          title = "NHF1 8h C>T All Reps TGG-Filtered Strand-Aligned",
                          xAxisLabel = "Dyad-Relative Position", xlim = c(-100, -40),
                          secondaryAxisBreaks = seq(19,19.8,0.2),
                          meanCutSiteDistanceMax = 19.825, meanCutSiteDistanceMin = 18.975)
```
```{r figure_S16C}
plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances$`8h`$three_prime,
                          FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
                          countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
                          meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances$`1h`$five_prime,
                          cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
                          title = "NHF1 8h C>T All Reps TGG-Filtered Strand-Aligned",
                          xAxisLabel = "Dyad-Relative Position", xlim = c(40, 100),
                          secondaryAxisBreaks = seq(19,19.8,0.2),
                          meanCutSiteDistanceMax = 19.825, meanCutSiteDistanceMin = 18.975)
```
